Type theory in type theory with single substitutions

### 2024-09-18 types_2024_postproc/p.tex
stuff

using typing judgements. B-systems are an intrinsic, but essentially

@@

relationship in more detail. B-systems are B-frames together with a

@@

homomorphism $\mathbb{S}$ corresponds to the following maps for the
bottom row of the diagram:

@@

operations for terms corresponding to the top row of the
diagram. Analogously, the weakening operation corresponds to

>>>>

using typing judgements. B-systems are an intrinsic, essentially

@@

relationship in more detail. B-systems are B-frames together with

@@

homomorphism $\mathbb{S}$ corresponds to the following maps for $\Ty$
(mapping between the bottom rows of the diagrams):

@@

operations for terms (top rows of the
diagrams). Analogously, the weakening operation corresponds to
